Nail: A practical interface generator for data formats

### 2014-09-09 paper/osdi14/relwk.tex
Typos
fix some undefined citations and other compile errors

Generating parsers and generators from an executable specification is the
core concept of interface generators, such as CORBA~\cite{omg:corba},
XDR~\cite{rfc:1832}, and Protocol Buffers~\cite{varda2008}.  However,
interface generators do not allow the programmer to specify the byte-level
data format; instead, they define their own data encoding that is
specific to a particular interface generator.  For instance, XDR-based
protocols are incompatible with Protocol Buffers.  Moreover, this means
that interface generators cannot be used to interact with existing protocols
that were not defined using that interface generator in the first place.
As a result, interface generators cannot be used to parse or generate
widely used formats such as DNS or ZIP, which is a goal for Nail.

Closely related work has been done in the field of data description languages, for example
PacketTypes~\cite{mccann2000packet} and DataScript~\cite{DataScript}. However, PacketTypes works
only as a parser, not as an output generator and implement a C-like structure model enhanced with
length fields and constraints. DataScript adds output generation and built-in support for offset
fields. However, these systems cannot handle complicated encodings such as compressed data, which
are supported by Nail's stream transforms. Many built-in features of these date description
languages, such as the various ways of encoding array size or length and offsets, can be expressed
by Nail transformations, keeping the core language itself smaller and increasing flexibility.

>>>>

Generating parsers and generators from an executable specification is the
core concept of interface generators, such as CORBA~\cite{omg:corba},
XDR~\cite{RFC:1832}, and Protocol Buffers~\cite{varda2008}.  However,
interface generators do not allow the programmer to specify the byte-level
data format; instead, they define their own data encoding that is
specific to a particular interface generator.  For instance, XDR-based
protocols are incompatible with Protocol Buffers.  Moreover, this means
that interface generators cannot be used to interact with existing protocols
that were not defined using that interface generator in the first place.
As a result, interface generators cannot be used to parse or generate
widely used formats such as DNS or ZIP, which is a goal for Nail.

Closely related work has been done in the field of data description languages, for example
PacketTypes~\cite{mccann2000packet} and DataScript~\cite{back2002datascript}.
A broader overview of data
description languages can be found in~\cite{Fisher:700DDL}. However, PacketTypes works
only as a parser, not as an output generator and implement a C-like structure model enhanced with
length fields and constraints. DataScript adds output generation and built-in support for offset
fields. However, these systems cannot handle complicated encodings such as compressed data, which
are supported by Nail's stream transforms. Many built-in features of these date description
languages, such as the various ways of encoding array size or length and offsets, can be expressed
by Nail transformations, keeping the core language itself smaller and increasing flexibility.
